Probabilistic Policy Violation Detection with IPFWD

### 2017-02-01 paper/main.tex
Add table for test systems, explain tests

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[journal]{IEEEtran}
\usepackage{blindtext}
\usepackage{graphicx}

@@

\section{Benchmarking Performance}
% Explain different systems
% Explain tools
% Explain rationale for choosing tools
\blindtext

>>>>

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[journal]{IEEEtran}
\usepackage{blindtext}
\usepackage{graphicx}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

@@

\section{Benchmarking Performance}
% Explain different systems
Tests were run on three different systems and five different network cards.

\begin{tabular}{ | l | L{19em} | } 
 \hline
 \multicolumn{2}{|c|}{Isilon OneFS 40Gb System} \\
 \hline
 \hline
 OS  &  FreeBSD 11 Release \\
 CPU &  8 x64 Intel\textsuperscript{\textregistered}\ Xeon\textsuperscript{\textregistered}\ CPU @ 2.20GHz \\
 MEM &  64Gb \\
 NIC &  Ethernet 40Gbase-T \\ 
 \hline
\end{tabular}\\\\

\begin{tabular}{ | l | L{19em} | } 
 \hline
 \multicolumn{2}{|c|}{Isilon OneFS 10Gb System} \\
 \hline
 \hline
 OS  &  FreeBSD 11 Release \\
 CPU &  8 x64 Intel\textsuperscript{\textregistered}\ Xeon\textsuperscript{\textregistered}\ CPU @ 2.20GHz \\
 MEM &  64Gb RAM \\
 NIC &  Ethernet 10Gbase-T \\ 
 \hline
\end{tabular} \\\\

\begin{tabular}{ | l | L{19em} | } 
 \hline
 \multicolumn{2}{|c|}{ WWU 10Gb System } \\
 \hline
 \hline
 OS  &  FreeBSD 11 Release \\
 CPU &  8 x64 Intel\textsuperscript{\textregistered}\ Core\texttrademark\ i7-2600 CPU @ 3.4GHz \\
 MEM &  16Gb \\ 
 NIC &  ??? \\ 
 \hline
\end{tabular} \\\\

\begin{tabular}{ | l | L{19em} | } 
 \hline
 \multicolumn{2}{|c|}{ WWU 1Gb System } \\
 \hline
 \hline
 OS  &  FreeBSD 11 Release \\
 CPU &  8 x64 Intel\textsuperscript{\textregistered}\ Core\texttrademark\ i7-2600 CPU @ 3.4GHz \\
 MEM &  16Gb \\
 NIC &  Ethernet 1000baseT \\ 
 \hline
\end{tabular} \\\\

\begin{tabular}{ | l | L{19em} | } 
 \hline
 \multicolumn{2}{|c|}{ Virtualized 10G System } \\
 \hline
 \hline
 OS  &  FreeBSD 11 Release \\
 CPU &  1 x64 Intel\textsuperscript{\textregistered}\ Xeon\textsuperscript{\textregistered}\ CPU @ 1.80GHz \\
 MEM &  512Mb \\
 NIC &  Ethernet 10Gbase-T \\ 
 \hline
\end{tabular} \\\\

The systems tested all used 64bit FreeBSD 11 Release, with varying CPU type, CPU speed, RAM and network cards. Isilon and WWU systems were both physical hardware, while the Virtualized system was in a hypervisor environment.

Virtualization makes it more difficult to have the same confidence in the results as with the physical machines. To account for this, tests on the Virtualized system were repeated additional times to account for the variability of the underlying physical hardware and contention between virtual machines.

The WWU and Virtualized tests were conducted on stock FreeBSD 11 without additional network performance configuration applied. Isilon OneFS does contain additional network performance tuning and demonstrates the additional gains IPFWD can provide with careful FreeBSD 11 kernel configuration.

% Explain tools
Multiple network performance tools were explored but the final results were compiled using Netperf. Netperf was chosen because it was readily available on all test platforms, provides built-in CPU utilization measurement, and a wide range of test types.

% Explain tests
The test type UDP\_STREAM was chosen over TCP\_STREAM for simplicity and to preserve CPU cycles for IPFW. Raw network throughput and CPU performance is the target metric, which can be difficult to assess with TCP without performance tuning. (REFERENCE)

All tests were conducted using the following steps:
\begin{enumerate}
    \item Machine 1
    \begin{enumerate}
        \item ipfw
        \item netserver
        \item CPU monitor
    \end{enumerate}
    \item Machine 2
    \begin{enumerate}
        \item ipfw
        \item ipfwd
        \item netperf
        \item CPU monitor
    \end{enumerate}
\end{enumerate}

All tests were run with minimal IPFW rule sets. Inituitively, larger
production rule sets would benefit even further from IPFWD.
